HL-LHC Computing Review:\\Common Tools and Community Software

### 2020-08-25 LHCC/2020/2020-01/input_simulation.tex
Generation text and references, sim references
Update some of the text on event sampling and negative weights
for event generation

Add a few references to simulation and generation sections

(Suggested by Ben Nachman)

Recent developments of deep
learning-based techniques have opened up an exciting possibility of
replacing those `classical' parameterisations by trained neural networks
that would reproduce the detector response. This approach consists of
training generative models, such as Generative Adversarial Networks
(GAN), Variational Auto-Encoders (VAE) or Autoregressive Generative
Networks on the `images' of particle 
showers~\cite{ML001-GAN, aishik_ghosh_2019_3599705, GAN-ATLAS}. The energy
deposition values in the calorimeter cells are considered as `pixels' of
the images that the network is supposed to reproduce. The first studies
and prototypes have shown very promising results, however, the
generalisation of the developed models (for different calorimeters, with
different particles incident at different angles with different
energies), still requires further effort. Detailed physics validation of
those tools and understanding their capability to reproduce
fluctuations is a prerequisite towards production quality fast
simulation libraries. This work is already ongoing, but will require,
over the next few years, more effort to be invested, combining
physics and Machine Learning expertise. Given that the training of the
deep learning algorithms usually requires using sufficiently large MC
samples produced using standard techniques, the development of these novel
tools does not necessarily remove the need to speed up Geant4.

@@

All LHC experiments have explored the use of multi-objective regression
and generative adversarial networks (GANs)~\cite{GAN-ATLAS, GAN-LHCb}, they are now in the process of investigating the use of
fast simulations for other types of detectors than calorimeters, e.g.
Cerenkov based systems~\cite{Lamarr} and Time Projection Chambers~\cite{ALICE-TPC}. While implementations of fast simulations of given
sub-detectors is specific to their technology and experimental
environment and as such the responsibility of each LHC experiment, an
area of potential common investigation is frameworks for fast tuning and
validation.

>>>>

Recent developments of deep
learning-based techniques have opened up an exciting possibility of
replacing those `classical' parameterisations by trained neural networks
that would reproduce the detector response. This approach consists of
training generative models, such as Generative Adversarial Networks
(GAN), Variational Auto-Encoders (VAE) or Autoregressive Generative
Networks on the `images' of particle 
showers~\cite{Paganini_2018, ML001-GAN, aishik_ghosh_2019_3599705, GAN-ATLAS}. The energy
deposition values in the calorimeter cells are considered as `pixels' of
the images that the network is supposed to reproduce. The first studies
and prototypes have shown very promising results, however, the
generalisation of the developed models (for different calorimeters, with
different particles incident at different angles with different
energies), still requires further effort. Detailed physics validation of
those tools and understanding their capability to reproduce
fluctuations is a prerequisite towards production quality fast
simulation libraries. This work is already ongoing, but will require,
over the next few years, more effort to be invested, combining
physics and Machine Learning expertise. Given that the training of the
deep learning algorithms usually requires using sufficiently large MC
samples produced using standard techniques, the development of these novel
tools does not necessarily remove the need to speed up Geant4.

@@

All LHC experiments have explored the use of multi-objective regression
and generative adversarial networks (GANs)~\cite{GAN-ATLAS, GAN-LHCb, aishik_ghosh_2019_3599705}, they are now in the process of investigating the use of
fast simulations for other types of detectors than calorimeters, e.g.
Cerenkov based systems~\cite{Lamarr} and Time Projection Chambers~\cite{ALICE-TPC}. While implementations of fast simulations of given
sub-detectors is specific to their technology and experimental
environment and as such the responsibility of each LHC experiment, an
area of potential common investigation is frameworks for fast tuning and
validation.
